### 2021-11-19 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@1f6ad5231268fff67c553a94829210342d470c00 🚀

The term \emph{ecological forecasting} implicitly creates an analogy
between predicting how ecosystems will change in the future by using the
term ``forecasting''---the most immediate analog is the success story of
forecasting is numerical weather prediction (NWP;
\textbf{Bauer2015QuiRev?}).

Much like ecology, NWP is faced with high-dimensional systems that are
governed by different mechanisms at different scales.

@@

\textbf{P5}

But forecasting isn't the only difficult problem here.

Transition to theme of optimization given unknown information. A
forecast gives us a range of future values with uncertainty around them.
Further a convenient property that a forecasting model's uncertainty
goes up over time (if we assume the underlying process is Markov--this
is a strong assumption but oft true of the models we fit to temporal
data)

In face of uncertainty, decision making is an optimization problem. We
have some goal state for the future, and some estimate of what the state
of the world will be given a set of actions. Frame optimization problem
mathematically an introduce concept of solution-space and constraint.

Indeed Marx's most well known quote that ``philosophers have hitherto
only interpreted the world in various ways; the point is to change it.''

and a necessary step toward establishing a just and sustainable world.

Transition to specifics of this thesis.

\begin{figure}
\centering
\includegraphics{./figures/thesisconcept.png}
\caption{thesis concept}
\end{figure}

>>>>

The term \emph{ecological forecasting} implicitly creates an analogy
between predicting how ecosystems will change in the future by using the
term ``forecasting''---the most immediate analog being the success story
of weather forecasting via numerical weather prediction (NWP).

Although it is become almost hack to complain about the dang weather
forecast being wrong, over the least 50 years the
(\textbf{Bauer2015QuiRev?}).

The success of NWP, and the Earth observations that support it should
serve as a template for development of a system for monitoring Earth's
biodiversity. Much like ecology, NWP is faced with high-dimensional
systems that are governed by different mechanisms at different scales.

@@

\begin{longtable}[]{@{}l@{}}
\toprule
\endhead
\begin{minipage}[t]{0.07\columnwidth}\raggedright
\textbf{P5}\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.07\columnwidth}\raggedright
But forecasting isn't the only difficult problem here.\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.07\columnwidth}\raggedright
Transition to theme of optimization given unknown information. A
forecast gives us a range of future values with uncertainty around them.
Further a convenient property that a forecasting model's uncertainty
goes up over time (if we assume the underlying process is Markov--this
is a strong assumption but oft true of the models we fit to temporal
data)\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.07\columnwidth}\raggedright
In face of uncertainty, decision making is an optimization problem. We
have some goal state for the future, and some estimate of what the state
of the world will be given a set of actions. Frame optimization problem
mathematically an introduce concept of solution-space and
constraint.\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.07\columnwidth}\raggedright
Indeed Marx's most well known quote that ``philosophers have hitherto
only interpreted the world in various ways; the point is to change
it.''\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.07\columnwidth}\raggedright
and a necessary step toward establishing a just and sustainable
world.\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

\begin{figure}
\hypertarget{fig:thesis}{%
\centering
\includegraphics{./figures/thesisconcept.png}
\caption{thesis concept}\label{fig:thesis}
}
\end{figure}

\textbf{P6 -- final intro para}

Three major components here: 1) Ecosystem monitoring, 2) Forecasting
using the products of that monitoring, and 3) Choosing the best possible
mitigation strategy.

This flow is outlined in the left panel of fig.~\ref{fig:thesis}
